Why Donors Donate?

### 2020-09-19 analysis/05_market_simulator.Rmd
Revert "Persona input mistakes corrected"
This reverts commit bf6eb23043fe7377012c1d3ada2a4fe979faac2d.

                        "Very little trust in political institutions",
                        "Little trust in political institutions",
                        "Nuetral trust in political institutions",
                        "Some trust in political institutions",
                        "A lot of trust in political institutions",
                        "Complete trust in political institutions",

@@

                        "Donate at least once a month", 

@@

                        "Active consumer member",

@@

textInput("p1_id",
          label = "Persona name",
          value = "Persona 1",
          placeholder = "Enter persona name",
          width = "450px")

@@

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not often",
                     "Often"),
         selected = "Often",
         width = "450px")

@@

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

@@

selectInput("p1_charity_importance",
          label = "Charity importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

#Fix
selectInput("p1_trust_in_charity",
            label = "Charity trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

#Fix
selectInput("p1_donation_frequency",
         label = "Donation frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p1_donation_amount",
         label = "Donation amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

#Fix
selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

#Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

# fix
selectInput("p1_personal_activism",
         label = "Personal activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

#Fix
selectInput("p1_family_activism",
         label = "Family activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

#Fix
selectInput("p1_religious_member",
         label = "Church membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

#Fix
selectInput("p1_sport_member",
         label = "Sport or recreational membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")
#Fix
selectInput("p1_art_member",
         label = "Art, music, or educational membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")
#Fix
selectInput("p1_labor_member",
         label = "Labor union membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

#Fix
selectInput("p1_political_member",
         label = "Political party membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")
# Fix
selectInput("p1_environmental_member",
         label = "Environmental organization membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")
# Fix
selectInput("p1_professional_member",
         label = "Professional membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")
# Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian organization membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")

# Fix
selectInput("p1_consumer_member",
         label = "Consumer organization membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization",
         width = "450px")
# Fix
selectInput("p1_other_member",
         label = "Other organization membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization",
         width = "450px")

@@

selectInput("p1_marital_status",
         label = "Marital status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married",
         width = "450px")

@@

textInput("p2_id",
          label = "Persona name",
          value = "Persona 2",
          placeholder = "Enter persona name",
          width = "450px")

@@

selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not often",
                     "Often"),
         selected = "Often",
         width = "450px")

selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel",
         width = "450px")

@@

selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions",
         width = "450px")

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month",
         width = "450px")

@@

selectInput("p2_charity_importance",
          label = "Charity importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

selectInput("p2_trust_in_charity",
            label = "Charity trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

selectInput("p2_donation_frequency",
         label = "Donation frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p2_donation_amount",
         label = "Donation amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

selectInput("p2_volunteer_frequency",
         label = "Volunteer frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

selectInput("p2_personal_activism",
         label = "Personal activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

selectInput("p2_family_activism",
         label = "Family activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

selectInput("p2_religious_member",
         label = "Church membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

selectInput("p2_sport_member",
         label = "Sport or recreational membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")

selectInput("p2_art_member",
         label = "Art, music, or educational membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")

selectInput("p2_labor_member",
         label = "Labor union membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

selectInput("p2_political_member",
         label = "Political party membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")

selectInput("p2_environmental_member",
         label = "Environmental organization membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")

selectInput("p2_professional_member",
         label = "Professional membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")

selectInput("p2_humanitarian_member",
         label = "Humanitarian organization membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")

selectInput("p2_consumer_member",
         label = "Consumer organization membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization",
         width = "450px")

selectInput("p2_other_member",
         label = "Other organization membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization",
         width = "450px")

@@

selectInput("p2_marital_status",
         label = "Marital status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married",
         width = "450px")

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "2 year degree",
         width = "450px")

@@

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "White",
         width = "450px")

@@

textInput("p3_id",
          label = "Persona name",
          value = "Persona 3",
          placeholder = "Enter persona name",
          width = "450px")

@@

selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not often",
                     "Often"),
         selected = "Often",
         width = "450px")

selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel",
         width = "450px")

@@

selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions",
         width = "450px")

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month",
         width = "450px")

@@

selectInput("p3_charity_importance",
          label = "Charity importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

selectInput("p3_trust_in_charity",
            label = "Charity trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

selectInput("p3_donation_frequency",
         label = "Donation frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p3_donation_amount",
         label = "Donation amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

selectInput("p3_volunteer_12",
         label = "Volunteered in last 12 months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

selectInput("p3_volunteer_frequency",
         label = "Volunteer frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

selectInput("p3_personal_activism",
         label = "Personal activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

selectInput("p3_family_activism",
         label = "Family activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

selectInput("p3_religious_member",
         label = "Church membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

selectInput("p3_sport_member",
         label = "Sport or recreational membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")

selectInput("p3_art_member",
         label = "Art, music, or educational membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")

selectInput("p3_labor_member",
         label = "Labor union membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

selectInput("p3_political_member",
         label = "Political party membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")

selectInput("p3_environmental_member",
         label = "Environmental organization membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")

selectInput("p3_professional_member",
         label = "Professional membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")

selectInput("p3_humanitarian_member",
         label = "Humanitarian organization membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")

selectInput("p3_consumer_member",
         label = "Consumer organization membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization",
         width = "450px")

selectInput("p3_other_member",
         label = "Other organization membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization",
         width = "450px")

>>>>

                        "Very little trust in polticial institutions",
                        "Little trust in polticial institutions",
                        "Nuetral trust in polticial institutions",
                        "Some trust in polticial institutions",
                        "A lot of trust in polticial institutions",
                        "Complete trust in polticial institutions",

@@

                        "Donate At least once a month", 

@@

                        "Active sonsumer member",

@@

textInput("p1_id",
          label = "Persona Name",
          value = "Persona 1",
          placeholder = "Enter Persona Name",
          width = "450px")

@@

selectInput("p1_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"),
         selected = "Often",
         width = "450px")

@@

selectInput("p1_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

@@

selectInput("p1_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

#Fix
selectInput("p1_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

#Fix
selectInput("p1_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p1_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

#Fix
selectInput("p1_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

#Fix
selectInput("p1_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

# fix
selectInput("p1_personal_activism",
         label = "Personal Activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

#Fix
selectInput("p1_family_activism",
         label = "Family Activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

#Fix
selectInput("p1_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

#Fix
selectInput("p1_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")
#Fix
selectInput("p1_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")
#Fix
selectInput("p1_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

#Fix
selectInput("p1_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")
# Fix
selectInput("p1_environmental_member",
         label = "Environmental Org. Membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")
# Fix
selectInput("p1_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")
# Fix
selectInput("p1_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")

# Fix
selectInput("p1_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization",
         width = "450px")
# Fix
selectInput("p1_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization",
         width = "450px")

@@

selectInput("p1_marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married",
         width = "450px")

@@

textInput("p2_id",
          label = "Persona Name",
          value = "Persona 2",
          placeholder = "Enter Persona Name",
          width = "450px")

@@

selectInput("p2_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"),
         selected = "Often",
         width = "450px")

#Fix
selectInput("p2_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel",
         width = "450px")

@@

#Fix
selectInput("p2_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions",
         width = "450px")

selectInput("p2_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

# Fix
selectInput("p2_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month",
         width = "450px")

@@

selectInput("p2_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

#Fix
selectInput("p2_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

#Fix
selectInput("p2_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p2_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

#Fix
selectInput("p2_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

#Fix
selectInput("p2_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

# fix
selectInput("p2_personal_activism",
         label = "Personal Activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

#Fix
selectInput("p2_family_activism",
         label = "Family Activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

#Fix
selectInput("p2_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

#Fix
selectInput("p2_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")
#Fix
selectInput("p2_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")
#Fix
selectInput("p2_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

#Fix
selectInput("p2_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")
# Fix
selectInput("p2_environmental_member",
         label = "Environmental Org. Membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")
# Fix
selectInput("p2_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")
# Fix
selectInput("p2_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")

# Fix
selectInput("p2_consumer_member",
         label = "Consumer Org. Membership:",
         choices = c("Don't belong to consumer organization",
                     'Inactive consumer member',
                     'Active consumer member'),
         selected = "Don't belong to consumer organization",
         width = "450px")
# Fix
selectInput("p2_other_member",
         label = "Other Org. Membership:",
         choices = c("Don't belong to other organization",
                     'Inactive other member',
                     'Active other member'),
         selected = "Don't belong to other organization",
         width = "450px")

@@

selectInput("p2_marital_status",
         label = "Marital Status:",
         choices = c("Married",
                     "Widowed",
                     "Divorced",
                     "Separated",
                     "Never married"),
         selected = "Married",
         width = "450px")

selectInput("p2_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school graduate",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate or professional degree",
                     "Doctorate"),
         selected = "Some college",
         width = "450px")

@@

selectInput("p2_race",
         label = "Race(s):",
         choices = c('White',
                     'Black or African American',
                     'American Indian or Alaska Native',
                     'Asian',
                     'Native Hawaiian or Pacific Islander',
                     'Other (Race)'),
         multiple = TRUE,
         selected = "American Indian or Alaska Native",
         width = "450px")

@@

textInput("p3_id",
          label = "Persona Name",
          value = "Persona 3",
          placeholder = "Enter Persona Name",
          width = "450px")

@@

selectInput("p3_follow_gov",
         label = "Follow government & public affairs:",
         choices = c("Not Often",
                     "Often"),
         selected = "Often",
         width = "450px")

#Fix
selectInput("p3_travel_developing",
         label = "Travel to developing country:",
         choices = c("Doesn't travel", "Does travel"),
         selected = "Does travel",
         width = "450px")

@@

#Fix
selectInput("p3_institution_trust",
         label = "Political institution trust from none to complete:",
         choices = c("No trust at all in political institutions",
                     "Very little trust in political institutions",
                     "Little trust in political institutions",
                     "Nuetral trust in political institutions",
                     "Some trust in political institutions",
                     "A lot of trust in political institutions",
                     "Complete trust in political institutions"),
         selected = "Complete trust in political institutions",
         width = "450px")

selectInput("p3_others_charitable",
         label = "People should be more charitable:",
         choices = c("Strongly Disagree",
                     "Disagree",
                     "Somewhat disagree",
                     "Nuetral",
                     "Somewhat agree",
                     "Agree",
                     "Strongly agree"),
         selected = "Strongly agree",
         width = "450px")

# Fix
selectInput("p3_worship_attendance",
         label = "Worship service attendance:",
         choices = c("Not sure",
                     "Rarely attend services",
                     "Attend at least once a month"),
         selected = "Attend at least once a month",
         width = "450px")

@@

selectInput("p3_charity_importance",
          label = "Charity Importance:",
          choices = c("Not at all important",
                      "Very unimportant",
                      "Somewhat unimportant",
                      "Nuetral",
                      "Somewhat important",
                      "Very important",
                      "Essential"),
          selected = "Somewhat unimportant",
          width = "450px")

#Fix
selectInput("p3_trust_in_charity",
            label = "Charity Trust:",
            choices = c("No trust at all in charities",
                        "Very little trust in charities",
                        "Little trust in charities",
                        "Nuetral trust in charities",
                        "Some trust in charities",
                        "A lot of trust in charities",
                        "Complete trust in charities"),
            selected = "Complete trust in charities",
            width = "450px")

#Fix
selectInput("p3_donation_frequency",
         label = "Donation Frequency:",
         choices = c('Donate more than once a month, less than once a year',
                     'Donate at least once a month'),
         selected = "Donate at least once a month",
         width = "450px")

selectInput("p3_donation_amount",
         label = "Donation Amount:",
         choices = c("$1-$49",
                     '$50-$99',
                     '$100-$499',
                     '$500-$999',
                     '$1,000-$4,999',
                     '$5,000-$9,999',
                     '$10,000+'),
         selected = "$100-$499",
         width = "450px")

#Fix
selectInput("p3_volunteer_12",
         label = "Volunteered in last 12 Months:",
         choices = c("Haven't volunteered", "Have volunteered"),
         selected = "Have volunteered",
         width = "450px")

#Fix
selectInput("p3_volunteer_frequency",
         label = "Volunteer Frequency:",
         choices = c("Haven't volunteered in past 12 months",
                     "Rarely volunteer",
                     "Volunteer more than once a month, less than once a year",
                     "Volunteer at least once a month"),
         selected = "Volunteer at least once a month",
         width = "450px")

# fix
selectInput("p3_personal_activism",
         label = "Personal Activism:",
         choices = c('Not personally involved ',
                     'Personally involved'),
         selected = "Personally involved",
         width = "450px")

#Fix
selectInput("p3_family_activism",
         label = "Family Activism:",
         choices = c('Family not involved',
                     'Family involved'),
         selected = "Family involved",
         width = "450px")

#Fix
selectInput("p3_religious_member",
         label = "Church Membership:",
         choices = c("Don't belong to church membership",
                     'Inactive church member',
                     'Active church member'),
         selected = "Don't belong to church membership",
         width = "450px")

#Fix
selectInput("p3_sport_member",
         label = "Sport or Recreational Membership:",
         choices = c("Don't belong to sports membership",
                     'Inactive sports member',
                     'Active sports member'),
         selected = "Don't belong to sports membership",
         width = "450px")
#Fix
selectInput("p3_art_member",
         label = "Art, Music, or Educational Membership:",
         choices = c("Don't belong to educational membership",
                     'Inactive educational member',
                     'Active educational member'),
         selected = "Don't belong to educational membership",
         width = "450px")
#Fix
selectInput("p3_labor_member",
         label = "Labor Union Membership:",
         choices = c("Don't belong to union",
                     'Inactive union member',
                     'Active union member'),
         selected = "Don't belong to union",
         width = "450px")

#Fix
selectInput("p3_political_member",
         label = "Political Party Membership:",
         choices = c("Don't belong to party",
                     'Inactive party member',
                     'Active party member'),
         selected = "Active party member",
         width = "450px")
# Fix
selectInput("p3_environmental_member",
         label = "Environmental Org. Membership:",
         choices = c("Don't belong to environmental organization",
                     'Inactive environmental member',
                     'Active environmental member'),
         selected = "Don't belong to environmental organization",
         width = "450px")
# Fix
selectInput("p3_professional_member",
         label = "Professional Membership:",
         choices = c("Don't belong to professional membership",
                     'Inactive professional member',
                     'Active professional member'),
         selected = "Don't belong to professional membership",
         width = "450px")
# Fix
selectInput("p3_humanitarian_member",
         label = "Humanitarian Org. Membership:",
         choices = c("Don't belong to humanitarian organization",
                     'Inactive humanitarian member',
                     'Active humanitarian member'),
         selected = "Active humanitarian member",
         width = "450px")
